LAGOS lake depth

### 2020-07-07 figures/01_contrasts.Rmd
start bathy contrast panel

>>>>

```{r gg_effort, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE, results='hide', fig.height = 3.5}
# compare characteristics of bathy lakes versus overall lakes

# load LAGOSUS DEPTH
lg_raw <- lagosus_load("depth")$depth$depth
lg <- lg_raw %>%
  mutate(lagos_effort = 
           forcats::fct_collapse(lg_raw$lagos_effort, 
                                 bathymetry = "bathymetry", 
                                 other = c("LAGOSNE", "manual", "NLA")))

# jsta::gg_quantdot
gg_quantdot <- function(dt, grp, var){
  # dt <- mtcars; grp <- "cyl"; var <- "mpg"

  # https://tbradley1013.github.io/2018/10/01/calculating-quantiles-for-groups-with-dplyr-summarize-and-purrr-partial/
  p       <- c(0.05, 0.5, 0.95)
  p_names <- paste0(as.character(p*100), "%")
  p_funs  <- lapply(seq_along(p), function(x){
    function(...){quantile(probs = p[x], na.rm = TRUE, ...)}
    })
  p_funs <- setNames(p_funs, p_names)

  dt %>%
    group_by({{grp}}) %>%
    summarise_at({{var}}, p_funs) %>% 
    ggplot() + 
    geom_pointrange(aes(x = {{grp}}, y = .data$`50%`,
                      ymin = .data$`5%`, ymax = .data$`95%`)) +
    ylab(var)
}

cowplot::plot_grid(
  gg_quantdot(lg, lagos_effort, "lake_maxdepth_m"), 
  gg_quantdot(lg, lagos_effort, "lake_waterarea_ha") +
    scale_y_log10(), 
  ncol = 1)

# library(tigris)
# urbanareas <- tigris::urban_areas()
# urbanareas <- st_as_sf(urbanareas)
# urbanareas <- st_transform(urbanareas, LAGOSUSgis:::albers_conic())
# urbanareas <- tidyr::separate(urbanareas, NAME10,
#                               c("urban_name", "urban_state"), sep = ", ")
# urbanareas <- dplyr::filter(urbanareas, !(urban_state %in% c("AK", "HI")))
# saveRDS(urbanareas, "../data/urbanareas.rds")
urbanareas <- readRDS("../data/urbanareas.rds")

test <- apply(st_distance(LAGOSUS::coordinatize(lg, crs = LAGOSUSgis:::albers_conic()),
            urbanareas), 1, function(x) x[which.min(x)])
```
